\chapter{}
\section{Introduction}
The statement "Smartphones have revolutionized the way we shop" is one that I believe to be true. To look into further depth behind my reasons for this, this report gives an insight into how much smartphones have developed in terms of shopping support, and how they have become a more prominent force in quicker purchases, advertising and ease of use for shoppers. Social, ethical and legal issues have also been considered in my decision, looking at what restrictions shopping through a smartphone may occur compared to contemporary face to face shopping. \par
As with any argument, an opposing opinion has also been considered, in order to back up my own personal choice by comparing the two.


\section{Key technologies in the shopping market} 
Technical- security, privacy, and payment means

Apps such as apple pay, android pay, wallets- These can make us impulse buy. Other apps such as deal apps, and online vouchers

One click buy on amazon, the ability to buy quickly, security implications

QR codes

Uses of location for unique discounts when entering shops

Mobile web sites with means of purchase, even if they are small and do not have an app

Browsing Internet at any time to be able to purchase on the fly- 4g

Deals, gambling and prices can be updates instantly in real time. Gets offers to users as soon as possible

Social media effects

Support from staff of companies to help customers

\section{Legal, social and ethical implications of key technologies}

Privacy of users, location and shopping habbits
Data protection act, Privacy acts etc.

Passwords on phones, being watched by others, or people see banking details

Security of QR codes?

\section{Arguments against revololutionary shopping through smartphones}

Entire population effected?
Age and ability of user?
Can it be better?

\section{Conclusion}

\begin{thebibliography}{1}
  
\bibitem{guidelines}
Apple, \emph{Human interface guidelines}, \hskip 1em plus
  0.5em minus 0.4em\relax \url{https://developer.apple.com/library/ios/documentation/UserExperience/Conceptual/MobileHIG/Navigation.html
}, 2016.

\bibitem{tabs}
Apple, \emph{Tab bar controllers}, \hskip 1em plus
  0.5em minus 0.4em\relax \url{https://developer.apple.com/library/ios/documentation/WindowsViews/Conceptual/ViewControllerCatalog/Chapters/TabBarControllers.html
}, 2016.

\bibitem{core-data}
P. Rea, \emph{Getting Started with Core Data Tutorial}, \hskip 1em plus
  0.5em minus 0.4em\relax \url{https://www.raywenderlich.com/115695/getting-started-with-core-data-tutorial
}, 2015.

\bibitem{core-data-apple}
Apple, \emph{Creating CoreData objects}, \hskip 1em plus
  0.5em minus 0.4em\relax \url{https://developer.apple.com/library/mac/documentation/Cocoa/Conceptual/CoreData/CreatingObjects.html
}, 2016.

\bibitem{game-play}
Stackoverflow- R. Roe, \emph{Shuffle an array in swift using GamePlayKit}, \hskip 1em plus
  0.5em minus 0.4em\relax \url{http://stackoverflow.com/questions/24026510/how-do-i-shuffle-an-array-in-swift
}, 2015.

\end{thebibliography}